Reducing Linearizability of Priority Queues and More Data Structures to State Reachability

### 2017-04-19 co-regular-EPQ.tex
modify

Register automata is a kind of finite automata with registers used to deal with infinite data domain, where register can be assigned values and do simple operations. In this paper we use a restricted kind of register automata, which contains only one register, whose value is obtained once by guessing and never changed. Our register machine contains a register $\textit{reg}$. Its transition labels are $\textit{call}(\textit{put},d,p,g), \textit{ret}(\textit{put},d,p),$ $\textit{call}(\textit{rm},d),\textit{ret}(\textit{rm},d)$, where $d \in \mathbb{D} \cup \{ \textit{empty} \}$, and $g$ and $\top$ are guards. A guard is a predicate chosen from $\{\textit{equalReg},\textit{lesReg},\top \}$, which represents equals the value of $\textit{reg}$, less than the value of $\textit{reg}$, and always holds, respectively. Given an execution $e = \alpha_1 \cdots \alpha_k$ of priority queue, register automata $\mathcal{A}$ accepts $e$, if there exists value $p \in \in \mathbb{D}$ and transitions $q_0 \xrightarrow{\beta_1} q_1 \ldots \xrightarrow{\beta_k} q_k$ of $\mathcal{A}$ from a initial state to a final state, such that for each $i$

\begin{itemize}
\setlength{\itemsep}{0.5pt}
\item[-] If $\alpha_i = \textit{call}(\textit{put},a,p)$, then $\beta_i= \textit{call}(\textit{put},a,p,g)$ and $g(q)$ holds.

>>>>

Register automata is a kind of finite automata with registers used to deal with infinite data domain, where register can be assigned values and do simple operations. In this paper we use a restricted kind of register automata, which contains only one register, whose value is obtained once by guessing and never changed. Our register machine contains a register $\textit{reg}$. Its transition labels are $\textit{call}(\textit{put},d,g), \textit{ret}(\textit{put},d,p),$ $\textit{call}(\textit{rm},d),\textit{ret}(\textit{rm},d)$, where $d \in \mathbb{D} \cup \{ \textit{empty} \}$, and $g$ and $\top$ are guards. A guard is a predicate chosen from $\{\textit{equalReg},\textit{lesReg},\top \}$, which represents equals the value of $\textit{reg}$, less than the value of $\textit{reg}$, and always holds, respectively. Given an execution $e = \alpha_1 \cdots \alpha_k$ of priority queue, register automata $\mathcal{A}$ accepts $e$, if there exists value $p \in \in \mathbb{D}$ and transitions $q_0 \xrightarrow{\beta_1} q_1 \ldots \xrightarrow{\beta_k} q_k$ of $\mathcal{A}$ from a initial state to a final state, such that for each $i$

\begin{itemize}
\setlength{\itemsep}{0.5pt}
\item[-] If $\alpha_i = \textit{call}(\textit{put},a,p)$, then $\beta_i= \textit{call}(\textit{put},a,g)$ and $g(q)$ holds.
